---
title: "Simulation of the AR(1) process"
author: "Katrine Holde"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation of the AR(1) process}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is an introduction in how to use the AR1 package. The package contains a few functions that can fx simulate a AR(1) process. 

### Installing
A quick guide on how to install the package. Use the function install.package() to download it and then load it with;
```{r}
library("AR1")
```


### Examples of how to use the simulation function
We will here show an example, that should visualize how to use the function. Here we have a AR(1) process, $$Y_{n+1}=\varphi Y_n+\varepsilon_n$$ where the white noise, $\varepsilon_n$, is a process with zero mean and variance 1 and the parameter and t distribution with 1.5 degrees of freedom, and $\varphi = 0.8$. Futhermore we have that $Y_0=0$. 

```{r, echo=FALSE, fig.width=3, fig.height=3, fig.show='hold'}
y <- simAR1(0, 300, 0.8, distfun = rnorm, 300)
plot(y, type = "l", main = "Normal distribution")
x <- simAR1(0, 300, 0, distfun = rt, 300, 1.5)
plot(y, type = "l", main = "t distribution")
```

### Examples of the Law of Large Numbers function and the Central Limit Theorm function
The function LLN() will help determine if there is a Law of Large Numbers. The function also plots the mean. CLT() helps determine if $$\frac{\sum_{i=1}^n Y_i}{\sqrt{n}}$$ converges in distribution as $n\to\infty$ to a normal distribution. Here is an example of how to use the two functions:   
```{r, echo=FALSE, fig.width=3, fig.height=3, fig.show='hold'}
x <- replicate(10, simAR1(0, 5000, 0.8, rnorm, 5000))
LLN(x)
w <- replicate(50000,simAR1(0, 1000, 0.8, rnorm, 1000))
CLT(w)
```
